Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-06-27 doc/bcspaper/article.tex
Updated reference to Alex C's pdfx paper

\subsection*{Paper Processing and classification}
%Discuss in more detail how Partridge processes papers (PDFX, sentence splitting) 
In order to obtain automatic labeling of sentences in a paper with
CoreSC concepts we first needed to convert the papers to a format that
the the CoreSC classifier, SAPIENTA can analyse.  Currently, SAPIENTA
supports the SciXML and PubMed Central DTDs.  Papers in PDF format are
first converted to XML using PDFX %\cite{PDFX} - no paper known yet
, a free service hosted by the University of Manchester
(\url{http://pdfx.cs.man.ac.uk/}). Once the paper has been split into
sentences, SAPIENTA is used to annotate each sentence with a relevant
CoreSC label. These labels are assigned using a conditional random
fields model based upon a number of features such as the sentence's
location within the paper and pairs and triplets of words found
consecutively within the sentence \cite{Liakata2012}.  The SAPIENTA
system has been trained on a corpus of 265 chemistry and biochemistry
papers and we have done no domain adaptation for the papers in PLoS.

>>>>

\subsection*{Paper Processing and classification}
%Discuss in more detail how Partridge processes papers (PDFX, sentence splitting) 
In order to obtain automatic labeling of sentences in a paper with
CoreSC concepts we first needed to convert the papers to a format that
the the CoreSC classifier, SAPIENTA can analyse.  Currently, SAPIENTA
supports the SciXML and PubMed Central DTDs.  Papers in PDF format are
first converted to XML using PDFX %\cite{PDFX} - no paper known yet
, a free service hosted by the University of Manchester
(\cite{Constantin2013}). Once the paper has been split into
sentences, SAPIENTA is used to annotate each sentence with a relevant
CoreSC label. These labels are assigned using a conditional random
fields model based upon a number of features such as the sentence's
location within the paper and pairs and triplets of words found
consecutively within the sentence \cite{Liakata2012}.  The SAPIENTA
system has been trained on a corpus of 265 chemistry and biochemistry
papers and we have done no domain adaptation for the papers in PLoS.
